\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-11-28 doc/paper-jss/sdmTMB-paper.Rnw
add check on CI for main effect of NAO

In addition to the output seen for other models, we now have a section for random intercepts and a standard deviation for the spatially varying coefficient random field.
Given our model specification, all random fields are sharing a single Matérn range.

@@

The spatially varying coefficient effect at any point in space is the combination of the main effect and spatially varying random effect for \code{nao}.
Mean estimates of the spatially varying random effect are available in the output of \fct{predict.sdmTMB} in a column starting with \code{zeta\_s} (in this case would appear as \code{zeta\_s\_nao}).
However, we might wish to combine the fixed and random components of a spatially varying effect and assess the uncertainty of these combined predictions.
We illustrate a way of accomplishing this by simulating from the parameter precision matrix assuming the joint parameter covariance matrix is multivariate normal.
We do this by specifying a non-null number of simulation draws to \code{nsim} in \fct{predict.sdmTMB}.
By default, \code{nsim > 0} will return a matrix of draws for the overall prediction.
Here, we instead specify that we want to return draws for the \code{zeta\_s} ($\zeta_{\bm{s}}$) random field, which is the spatially varying random field.
This returns a matrix where each row matches a row of \code{newdata} and each column is a simulation draw.
We then use the function \fct{spread\_sims} to draw 200 simulations for the parameters themselves.
Because the simulations are stored in different dimensions for these two functions, the random field draws must be transposed \code{t()} before combining the main effect draws (\code{sims\$nao}) with the random field values \code{zeta\_s}.
Next, we can calculate the median, and upper and lower quantiles for each column of data, which correspond to the rows in the data provided.
For this example we use thresholds of 0.1 and 0.9 representing confidence intervals (CI) of 80\%.

>>>>

In addition to the output seen for other models, we now have a section for random intercepts and a standard deviation for the spatially varying coefficient random field.
Given our model specification, all random fields are sharing a single Matérn range.
We can also check the confidence intervals (CIs) on the main effect of NAO and see that they overlap zero.

<<owl-tidy, echo=TRUE>>=
tidy(fit_owl, conf.int = TRUE)
@

But given that this is only part of the effect of NAO that we include in our model, how do we assess if this variable has a meaningful effect in some locations, even if not overall?

@@

The spatially varying coefficient effect at any point in space is the combination of the main effect and spatially varying random effect for \code{nao}.
Mean estimates of the spatially varying random effect are available in the output of \fct{predict.sdmTMB} in a column starting with \code{zeta\_s} (in this case would appear as \code{zeta\_s\_nao}).
However, we might wish to combine the fixed and random components of a spatially varying effect and assess the uncertainty of these combined predictions.
We illustrate a way of accomplishing this by simulating from the parameter precision matrix assuming the joint parameter covariance matrix is multivariate normal.
We do this by specifying a non-null number of simulation draws to \code{nsim} in \fct{predict.sdmTMB}.
By default, \code{nsim > 0} will return a matrix of draws for the overall prediction.
Here, we instead specify that we want to return draws for the \code{zeta\_s} ($\zeta_{\bm{s}}$) random field, which is the spatially varying random field.
This returns a matrix where each row matches a row of \code{newdata} and each column is a simulation draw.
We then use the function \fct{spread\_sims} to draw 200 simulations for the parameters themselves.
Because the simulations are stored in different dimensions for these two functions, the random field draws must be transposed \code{t()} before combining the main effect draws (\code{sims\$nao}) with the random field values \code{zeta\_s}.
Next, we can calculate the median, and upper and lower quantiles for each column of data, which correspond to the rows in the data provided.
For this example we use thresholds of 0.1 and 0.9 representing CIs of 80\%.
